Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-08 introduction.tex

\begin{example}[Running example]
Throughout the paper we
illustrate our framework with music transcription examples: Given
a \emph{timeline} of musical events with arbitrary timestamps as input, parse it
into a structured music score. In our example, input events
are pairs $\< \eta, \tau>$ made of
a symbol $\eta \in \Sigma$, where $\Sigma$ stands for the
set of MIDI message symbols~\cite{?}
and  $\tau \in \mathbb{Q}$ is a timestamp. The output of parsing
is a representation of the sequence in
Common Western Music Notation (CWMN)~\cite{Gould11Notation}
where event symbols belong to the domain $\Delta$
of \emph{pitches} (e.g., A4, G5, etc.), temporal
information is encoded as \emph{durations} (whole \musWhole$,
$quarter, $\musQuarter$, eight $\musEighth$, etc), and notes are grouped in
high-level structures (beams, measures, tuplets). The following inputs
will be used:
\begin{enumerate}
  \item $I_1  = [ \<e_1, 0.07>,\<e_2, 0.72>, \<e_3, 0.91>]$, over interval $[0,1[$
  \item $I_2  = [ \<e_3, 1.05>,\<e_4, 1.36>, \<e_5, 1.71>]$, over interval $[1,2[$
\end{enumerate}
There exists many possible parsings of $I_1 \cup I_2$ in music notation, among
which
\includegraphics[scale=0.20]{pictures/score5.png}
and \includegraphics[scale=0.20]{pictures/score4.png}.  
SW-parsing associates a cost 
\florent{weight value}
to each solution, and our framework
aims at selecting the best one with respect to this cost.
\endex
\end{example}

>>>>

\begin{example}[Running example]\label{ex:running}
Throughout the paper we
illustrate our framework with music transcription examples: Given
a \emph{timeline} of musical events with arbitrary timestamps as input, parse it
into a structured music score. In our example, input events
are pairs $\< \eta, \tau>$ made of
a symbol $\eta \in \Sigma$, where $\Sigma$ stands for the
set of MIDI message symbols~\cite{?}
and  $\tau \in \mathbb{Q}$ is a timestamp. The output of parsing
is a representation of the sequence in
Common Western Music Notation (CWMN)~\cite{Gould11Notation}
where event symbols belong to the domain $\Delta$
of \emph{pitches} (e.g., A4, G5, etc.), temporal
information is encoded as \emph{durations} (whole \musWhole$,
$quarter, $\musQuarter$, eight $\musEighth$, etc), and notes are grouped in
high-level structures (beams, measures, tuplets). The following inputs
will be used:
\begin{enumerate}
  \item $I_1  = [ \<e_1, 0.07>,\<e_2, 0.72>, \<e_3, 0.91>]$, over interval $[0,1[$
  \item $I_2  = [ \<e_3, 1.05>,\<e_4, 1.36>, \<e_5, 1.71>]$, over interval $[1,2[$
\end{enumerate}
There exists many possible parsings of $I_1 \cup I_2$ in music notation, among
which
\includegraphics[scale=0.20]{pictures/score5.png}
and \includegraphics[scale=0.20]{pictures/score4.png}.  
SW-parsing associates a cost 
\florent{weight value}
to each solution, and our framework
aims at selecting the best one with respect to this cost.
\endex
\end{example}

### 2021-07-08 semiring.tex

\begin{example}
The recursive subdivision of time that leads to hierarchichal
structures of music notation can be modeled as
production rules. Since there exists several possible division,
rules can be weighted 
in the tropical semiring whose domain $\mathbb{R}_+ \cup \{ +\infty\}$,
$\oplus$ is min, $\zero = +\infty$, $\otimes$ is sum, and $\one = 0$.
For instance, the following production rules define two possible divisions
of a bounded time interval into respectively a duplet and a triplet.
\[
\rho_1: q_0 \xrightarrow{0.06} \< q_{1}, q_{2}>,\
\rho_2: q_0 \xrightarrow{0.12} \< q_{1}, q_{2}, q_{2}>.
\]
\endex
\end{example}
%%% semiring properties used in paper
% - commutative
% - bounded (implies idempotent and superior)
% - total
% - complete

>>>>

\begin{example}\label{rules-division}
The recursive subdivision of time that leads to hierarchichal
structures of music notation can be modeled as
production rules. Since there exists several possible division,
rules can be weighted
in the tropical semiring whose domain $\mathbb{R}_+ \cup \{ +\infty\}$,
$\oplus$ is min, $\zero = +\infty$, $\otimes$ is sum, and $\one = 0$.
For instance, the following production rules define two possible divisions
of a bounded time interval into respectively a duplet and a triplet.
\[
\rho_1: q_0 \xrightarrow{0.06} \< q_{1}, q_{2}>,\
\rho_2: q_0 \xrightarrow{0.12} \< q_{1}, q_{2}, q_{2}>.
\]
Further binary divisions of time sub-intervals %represented respectively by~$q_2$ and~$q_3$
are possible with:

\[
\rho_3:\,q_2 \xrightarrow{0.1} \< q_{3}, q_{3}>, \
\rho_4:\,q_3 \xrightarrow{0.11} \< q_{4}, q_{4}>. \
\]

\endex
\end{example}
%%% semiring properties used in paper
% - commutative
% - bounded (implies idempotent and superior)
% - total
% - complete
